\documentclass[11pt]{article}
\usepackage{hyperref}
\parindent 0px

\title{My \LaTeX\ Document}
\author{Charlie Watts}
\date{\today}

\begin{document}
\tableofcontents
\maketitle

This is normal text.\\
This is \textit{italicized} text.\\
This will produced \textbf{bold faced} text.\\
This will produce \textsc{small caps} text.\\
This will produce \texttt{typewriter font} text.\\

Please visit the following website at \texttt{http://www.yahoo.com}.\\
Please visit the following website at \url{http://www.yahoo.com}.\\
Please visit my site at \href{https://www.yahoo.com}{Yahoo!}.\\

\vspace{0.5 cm}

Please excuse my dear aunt Sally.

Please excuse my \begin{large}dear aunt Sally.
\end{large}

Please excuse my \begin{Large}dear aunt Sally.
\end{Large}

Please excuse my \begin{huge}dear aunt Sally.
\end{huge}

Please excuse my \begin{Huge}dear aunt Sally.
\end{Huge}

Please excuse my \begin{normalsize}dear aunt Sally.
\end{normalsize}

Please excuse my \begin{small}dear aunt Sally.
\end{small}

Please excuse my \begin{scriptsize}dear aunt Sally.
\end{scriptsize}

Please excuse my \begin{tiny} aunt Sally.
\end{tiny}

\vspace{1cm}

\begin{center}
This line is centered.
\end{center}

\begin{flushleft}
This line is left justified.
\end{flushleft}

\begin{flushright}
This line is right justified.
\end{flushright}

\tiny
This line is centered.

This line is left-justified.

This line is right-justified.

\section{Linear Functions}
	\subsection{Slope-Intercept Form}
		\subsubsection{Example 1:}
		\subsubsection{Example 2:}
	\subsection{Standard Form}
	\subsection{Point-Slope Form}
\section{Quadratic Functions}
	\subsection{Vertex Form}
	\subsection{Standard Form}
	\subsection{Factored Form}



\end{document}